Insurance choice, decision assistance, and insurer steering

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
correct ashecon slides
update ashecon slides

---
# 1. Insurance choice is confusing

.center[
  ![](../pics/slate-2017.png)
]

.footnote[
  [Slate, 2017](https://slate.com/business/2017/08/americans-are-overpaying-for-insurance-because-obamacare-is-confusing.html)
]

# 1. Insurance choice is confusing
.center[
  ![](../pics/health-affairs-2017b.png)
]

.footnote[
  [Health Affairs, January, 2017](https://www.healthaffairs.org/doi/10.1377/hlthaff.2016.0472)
]

# 1. Insurance choice is confusing

.center[
  ![](../pics/health-affairs-2017.png)
]

.footnote[
  [Health Affairs, August, 2017](https://www.healthaffairs.org/doi/full/10.1377/hlthaff.2017.0085)
]

---
# 2. Potential scale

- 12.7 million enrollees on exchanges in 2016

- Down to 11.4 million in 2020

- Over 27 million remain uninsured

# 2. Potential scale

.center[
  ![:scale 75%](../pics/kff-uninsured.png)
]

@@

1. Calculate predicted probability of decision assistance from logit model
2. Estimate weighted multinomial logit model among those without any decision assistance, $\hat{\theta}$, with weights $\frac{\hat{p}}{1-\hat{p}}$
3. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
4. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{ij}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}}_{Predicted}$$
5. Aggregate to level of insurer and metal

>>>>

@@

1. Calculate predicted probability of decision assistance from logit model
2. Estimate weighted nested logit model among those without any decision assistance, $\hat{\theta}$, with weights $\frac{\hat{p}}{1-\hat{p}}$
3. Use $\hat{\theta}$ to form predicted counterfactual, $\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}$
4. Use predicted value in ATT estimate: $$\underbrace{Pr[Y_{ij}^{1} | \text{Assist}]}_{Observed} - \underbrace{\widehat{Pr[Y_{ij}^{0} | \text{Assist}]}}_{Predicted}$$
5. Aggregate to level of insurer and metal
